---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
mydata <- read.csv("activity.csv")

```


## What is mean total number of steps taken per day?

```{r}
steps_per_day <- tapply(mydata$steps, mydata$date, sum,na.rm = T, simplify = T)
hist(steps_per_day)
```

The mean number of steps taken per day is `r round(mean(steps_per_day, na.rm = T),1)` and the median number of steps taken ped day is `r median(steps_per_day, na.rm = T)`.



## What is the average daily activity pattern?

```{r}
daily_activity <- tapply(mydata$steps, mydata$interval, sum,na.rm = T, simplify = T)

plot(daily_activity, type="l")

```

The `r which.max(daily_activity)` th interval contains on average the maximum number of steps (`r max(daily_activity, na.rm=T)`).

## Imputing missing values

The number of rows with missing values is `r sum(!complete.cases(mydata))`.

Imputing missing values using the daily avearge.

```{r}
mydata_imputed <- mydata
for (i in mydata$date)
{
  mean_steps <- round(mean(mydata$steps[mydata$date == i], na.rm = T),1)
  mydata_imputed[mydata_imputed$date == i & is.na(mydata_imputed$steps), 'steps'] <- mean_steps
  
}
```

```{r}
imputed_steps_per_day <- tapply(mydata_imputed$steps, mydata_imputed$date, sum,na.rm = T)
hist(imputed_steps_per_day)
```

The mean number of steps taken per day is `r round(mean(imputed_steps_per_day, na.rm = T),1)` and the median number of steps taken ped day is `r round(median(imputed_steps_per_day, na.rm = T),1)`.

The mean is the same (should be) as without imputing, the median is almost the same.
The total number of steps per day should increase as the impact of imputation.


## Are there differences in activity patterns between weekdays and weekends?

```{r}
mydata_imputed$date <- as.Date(mydata_imputed$date)
mydata_imputed$weekdays <- as.factor(ifelse(weekdays(mydata_imputed$date) == "Saturday" | weekdays(mydata_imputed$date) == "Sunday", "weekend", "weekday"))
steps_weekday <- tapply(mydata_imputed$steps, list(mydata_imputed$weekdays, mydata_imputed$interval), mean,na.rm = T)

par(mfrow=c(2,1))
plot(na.omit(steps_weekday[1,]), type = "l", ylab="Nb. of steps", main="Weekday")
plot(na.omit(steps_weekday[2,]), type = "l", ylab="Nb. of steps", main="Weekend")
par(mfrow=c(1,1))

```

